\Large{Learning to Pivot with Adversarial Networks}

### 2016-11-01 tex/paper.tex
save

In machine learning, learning a pivotal quantity can be related to the problem
of domain adaptation
\citep{blitzer2006domain,pan2011domain,gopalan2011domain,gong2013connecting,baktashmotlagh2013unsupervised,ajakan2014domain,ganin2014unsupervised},
where the goal is often stated as trying to learn a domain-invariant
representation of the data. Likewise, our method also relates to the problem of
enforcing fairness in classification \citep{zemel2013learning,feldman2015certifying,EdwardsS15,zafar2015fairness}, which
is stated as learning a classifier that is independent of some chosen attribute
such as gender, color or age. For both families of methods, the problem can
equivalently be stated as learning a classifier which is a pivotal quantity with
respect to either the domain or the selected feature. In this context,
\citep{ganin2014unsupervised,EdwardsS15} are certainly among the closest to our
work, in which domain invariance and fairness are enforced through an
adversarial minimax setup composed of a classifier and an adversary
discriminator.
Following this line of work and without making assumptions on the prior $p(Z)$, our method can be regarded as a
generalization that also supports a continuously parametrized family of domains or as enforcing fairness over continuous attributes.
In that sense, our work is also original in the theoretical characterization
of the minimax solution of Eqn.~\ref{eqn:min_thetaf}.

>>>>

In machine learning, learning a pivotal quantity can be related to the problem
of domain adaptation
\citep{blitzer2006domain,pan2011domain,gopalan2011domain,gong2013connecting,baktashmotlagh2013unsupervised,ajakan2014domain,ganin2014unsupervised},
where the goal is often stated as trying to learn a domain-invariant
representation of the data. Likewise, our method also relates to the problem of
enforcing fairness in classification \citep{zemel2013learning,feldman2015certifying,EdwardsS15,zafar2015fairness}, which
is stated as learning a classifier that is independent of some chosen attribute
such as gender, color or age. For both families of methods, the problem can
equivalently be stated as learning a classifier which is a pivotal quantity with
respect to either the domain or the selected feature. In this context,
\citep{ganin2014unsupervised,EdwardsS15} are certainly among the closest to our
work, in which domain invariance and fairness are enforced through an
adversarial minimax setup composed of a classifier and an adversary
discriminator.
Following this line of work and without making assumptions on the prior $p(Z)$, our method can be regarded as a
generalization that also supports a continuously parametrized family of domains or as enforcing fairness over continuous attributes.
In that sense, and to the best of our knowledge, our work is also original in the theoretical characterization
of the minimax solution of Eqn.~\ref{eqn:min_thetaf}, as well as in how one can trade-off accuracy for robustness through Eqn.~\ref{eqn:vf-lambda}.
